Commit Rater

### 2015-08-26 presentations/paper/methodology.tex
Describe author level analysis

% 1. Level: No use
% 2. Level: Commit Rater Web
% 3: Level: Boxplots

>>>>

\subsubsection{Author-level}
\label{subs:Author-level}
Analysis on this level evaluates the metrics-triples that were described in \ref{sec:data-synthesis}, where each author has a triple $(pass, fail, undef)$ for each criterion with $pass$ the number of commits that \emph{pass} the test for the criterion, $fail$ the number of commits that \emph{fail} the test for the criterion and $undef$ the number of commits that could not be tested against the criterion.

The rate of how many of the commits pass a certain criterion may be interpreted as the rate with wich the author adheres the corresponding rule. The rate is calculated with the following formula:

\begin{equation}
  \label{eq:rate}
  rate(triple) = \frac{triple_{pass}}{triple_{pass} + triple_{fail}}
\end{equation}

The important thing to note about this formula is, that it excludes $undef$. This means, that for instance authors who rarely use the body (see \ref{subs:body_used}) still have a useful refelction on how many of their commits with body were limited to 72 characters per line (\ref{subs:body_limit}).

An example: A author with the triple $(190, 10, 0)$ for the subject limit (\ref{subs:subject_limit}) successfully limits his subject lines to 50 characters in 95\% of his commits. It could therefore furthermore be concluded that he is aware of the guideline, but has no tool in place that would prevent accidentally writing more than 50 characters.

An average of these rates over all criteria can be seen as a general rating of an author's commit behaviour. Because of the $undef$s, two averages have to be considered: The standard average, which is just the average over the rates described above. And an average over the rates where each rate is weighted according to how many of all commits constituted to the rate. An author with a triple $(5, 5, 90)$ has a rate of 50\% according to equation \ref{eq:rate}, but should factor less into the average since only 10\% of all commits could be evaluated. Thus, the weighted average is calculated as follows:

\begin{equation}
  wa(triples) = \frac{1}{|triples|} \times \sum{t \element triples} rate(t) \times weight(t)
\end{equation}

Where triples is the collection of triples of an author and a weight is calculated as follows:

\begin{equation}
  weight(triple) = \frac{triple_{pass} + triple_{fail}}{triple_{pass} + triple_{fail} + triple_{undef}}
\end{equation}

When working on this level, it turned out to be useful to exclude authors with few commits (maybe 10 or less), since the analysis results for these authors are not representative enough to infer any interpretations.

This kind of analysis may be helpful for individual developers who seek to improve their Git etiquette. Because of this, we developed a web-frontend to our commit rater with integrated analysis. The source-code can be found on GitHub: \url{https://github.com/hartenfels/Commit-Rater-Web}

\TODO{Insert Screenshot of Commit Rater Web, maybe describe a little bit more}

\TODO{Level 3: Boxplots}
